Time stability in human interaction networks

### 2015-06-03 paper.tex
enhanced images
added new 3d plot
smaller text edits

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.5\textwidth]{figs/criaRede_}
	\caption{Formation of interaction network from email messages. Each vertex represents a participant. A reply message from participant B to a message from participant A is regarded as evidence that B received information from A and yields a directed edge. Multiple messages add ``weight'' to a directed edge. Further details are given in Section~\ref{intNet}.}
	\label{formationNetwork}
\end{figure}

@@

\subsection{Scalable fat-tail structure: constancy of membership fractions in the Erd\"os sectors}\label{subsec:pih}

@@

\begin{figure}
   \centering
        \includegraphics[width=\columnwidth]{figs/mpgamma____}
	\caption{A 3D scatter plot of messages (M) versus participants (N) versus threads ($\Gamma$) 140 email lists. The highest number of threads are found in lists with few participants. The correlation between $N$ and $\Gamma$ is negative for low values of $N$ but positive otherwise.}
	\label{fig:nmgamma3d}
\end{figure}

>>>>

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.5\textwidth]{figs/criaRede__}
	\caption{Formation of interaction network from email messages. Each vertex represents a participant. A reply message from participant B to a message from participant A is regarded as evidence that B received information from A and yields a directed edge. Multiple messages add ``weight'' to a directed edge. Further details are given in Section~\ref{intNet}.}
	\label{formationNetwork}
\end{figure}

@@

\subsection{Scalable fat-tail structure: constancy of membership fractions in each Erd\"os sector}\label{subsec:pih}

@@

\begin{figure}
   \centering
        \includegraphics[width=\columnwidth]{figs/mpgamma____________}
	\caption{A scatter plot of messages (M) versus participants (N) versus threads ($\Gamma$) of 140 email lists. The highest number of threads are found in lists with few participants. The correlation between $N$ and $\Gamma$ is negative for low values of $N$ but positive otherwise. This negative correlation between $N$ and $\Gamma$ can also be observed in Table~\ref{tab:genLists}. For $M=20000$ messages, positive correlation of $N$ and $\Gamma$ is present mostly above 1500 participants. All LAU, LAD, MET are smaller networks.}
	\label{fig:nmgamma3d}
\end{figure}
